Object-based Auditory Scenes Similarity Retrieval and Classification With Wavelet Scattering

### 2016-07-12 paper/structureScene.tex
more in VIII.B on DCASE 2016

The results on the evaluation dataset are awaiting publication by the DCASE organizing committee.
Our results on the development dataset are reported in Table \ref{table:dcase2016}

@@

This assertion shall be studied further in future work by considering more complex convolutional networks, larger databases and more diverse applications, such as pleasantness prediction \cite{lafaySoundscapePilot, lafayPartI} and other ecoacoustics tasks.

>>>>

Our results on the development dataset are reported in Table \ref{table:dcase2016}, in comparison with a baseline of $MFCCs$ coefficients and a generative classifier, namely Gaussian mixture models with $16$ Gaussians per model.
The average accuracy across classes is brought from $70.8\%$ to $79.4\%$.
It appears that log-scattering features compare favorably to 
The results on the evaluation dataset are awaiting publication by the DCASE organizing committee, and will be disclosed in August 2016.

@@

This assertion shall be studied further in future work by considering data-driven convolutional networks, larger databases and more diverse applications, such as pleasantness prediction \cite{lafaySoundscapePilot, lafayPartI} as well as other tasks in ecoacoustics.
